Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Edit background section

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
For these tasks, a popular approach is the bag-of-frames (BOF) approach for acoustic scene modeling introduced by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Being a very generic method, this approach has been applied to many audio classification tasks besides ASC.
Yet the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
Indeed, the typical morphology of acoustic scenes is a ``skeleton of events on a bed of textures'' \cite{nelken2013}, with a few discrete sound events superimposed upon a stationary acoustic background.
Therefore, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

@@

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task.
An overview of the efforts for the latter task is provided by the IEEE Audio and Acoustic Signal Processing (AASP) Detection and Classification of Acoustic Scenes and Events (DCASE) challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms as well as newer systems that use the private part of the DCASE 2013 dataset for their experiments. Most of the scene prediction results are achieved by majority voting of predictions over local features.

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} 
}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

>>>>

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
For these tasks, a popular approach is the bag-of-frames (BOF) approach for acoustic scene modeling introduced by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Interestingly, the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, which is a ``skeleton of events on a bed of textures'' \cite{nelken2013} where a few discrete sound events superimposed upon a stationary acoustic background.
Therefore, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

@@

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task.
An overview of the efforts for the latter task is provided by the IEEE Audio and Acoustic Signal Processing (AASP) Detection and Classification of Acoustic Scenes and Events (DCASE) challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification.

The methods that performed the best all followed a similar structure, where a low-level feature representation, such as MFCCs, were calculated over short windows and fed separately to a classifier, such as an SVM, for training. During the classification stage, the recording to be classified was similarly processed into short windows represented by feature vectors which were classified individually by the classifier and the classifier output was combined over the recording through majority vote. This last step is known as late integration and allows the classifier to work on individual, shorter-scale sound events instead of trying to classify the recording as a whole. By doing this, the classifier is able to identify and exploit the distinct events that characterize the scene instead of trying to model its average structure. This is in agreement with the psychoacoustic results related to the perception of auditory scenes presented above.
